\textbf{EECS 340: Assignment 1}

### 2020-01-26 assignment_1/article.tex
✨ Add sketch answer to Problem 2(b).
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>

\documentclass[12pt]{article}
\usepackage{setspace}
\setstretch{1.1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\inlinecode}{\texttt}
\usepackage{etoolbox}
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

@@

\subsection{(b)}
\subsection{(c)}
If $A[i] + B[j] \neq x$, then it is impossible to have any combination $(a, b)$ where \\ $a \in \{A[0], A[1], ..., A[i-1], A[i]\}$ and $b \in \{B[j], B[j+1], B[j+2], ..., B[n-1]\}$ to \\be $a + b = x$ for all \textbf{iterarted} $i, j$ within the \inlinecode{while} loop.

>>>>

\documentclass[12pt]{article}
\usepackage{setspace}
\setstretch{1.1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\inlinecode}{\texttt}
\usepackage{etoolbox}
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{matrix,positioning,arrows.meta,arrows}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

@@

\newpage

\subsection{(b)}

The following is graphical demenstration of \textit{TwoSum(A, B, 5, 12)}:
\tikzset{
mymat/.style={
  matrix of math nodes,
  text height=2.5ex,
  text depth=0.75ex,
  text width=3.25ex,
  align=center,
  column sep=-\pgflinewidth
  },
mymats/.style={
  mymat,
  nodes={draw,fill=#1}
  }
}

\begin{tikzpicture}[>=latex]

\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (0,0)
(mat1)
{
0 & 1 & 2(i) & 3 & 4 \\
1 & 3 & 5 & 7 & 9 \\
};

\matrix[mymat,right=of mat1,row 2/.style={nodes={draw,fill=gray!30}}]
at (10,0)
(mat2)
{
0 & 1 & 2 & 3(j) & 4 \\
2 & 4 & 6 & 7 & 10 \\
};

\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (0,2)
(mat3)
{
0 & 1(i) & 2 & 3 & 4 \\
1 & 3 & 5 & 7 & 9 \\
};
\matrix[mymat,right=of mat3,row 2/.style={nodes={draw,fill=gray!30}}]
at (10,2)
(mat4)
{
0 & 1 & 2 & 3(j) & 4 \\
2 & 4 & 6 & 7 & 10 \\
};

\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (0,4)
(mat5)
{
0 & 1(i) & 2 & 3 & 4 \\
1 & 3 & 5 & 7 & 9 \\
};
\matrix[mymat,right=of mat5,row 2/.style={nodes={draw,fill=gray!30}}]
at (10,4)
(mat6)
{
0 & 1 & 2 & 3 & 4(j) \\
2 & 4 & 6 & 7 & 10 \\
};

\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (0,6)
(mat7)
{
0(i) & 1 & 2 & 3 & 4 \\
1 & 3 & 5 & 7 & 9 \\
};
\matrix[mymat,right=of mat7,row 2/.style={nodes={draw,fill=gray!30}}]
at (10,6)
(mat8)
{
0 & 1 & 2 & 3 & 4(j) \\
2 & 4 & 6 & 7 & 10 \\
};

\node[above=0pt of mat7]
  (cella) {A};
\node[above=0pt of mat8]
  (cellb) {B};

\end{tikzpicture}\newline

Thus we have $A[i] + B[j] = 12$ for $(i, j)$ being $(2, 3)$.

\subsection{(c)}
If $A[i] + B[j] \neq x$, then it is impossible to have any combination $(a, b)$ where \\ $a \in \{A[0], A[1], ..., A[i-1], A[i]\}$ and $b \in \{B[j], B[j+1], B[j+2], ..., B[n-1]\}$ to \\be $a + b = x$ for all \textbf{iterarted} $i, j$ within the \inlinecode{while} loop.
